The \dealii{} Library, Version 9.0

### 2018-04-21 9.0/paper.tex
Reshuffle some of the sections.

@@

\item \dealii{} has made extensive use of both the Clang-Tidy \cite{clang-tidy}
  and Coverity Scan \cite{coverity} static analysis tools for detecting bugs
  and other issues in the code. In total around, 260 issues were detected and
  fixed using the latter tool.
      %% > Is there somewhere we can cite for either of these tools? It would
      %% > be nice to recognize the department of homeland security for offering
      %% The contract with homeland security was completed in 2009.

@@

\item
  Support for GPU
  \marginpar{paragraph for CUDA missing}

\item
  In this version we add template wrappers for ScaLAPACK -- parallel dense
  linear algebra library with block-cyclic matrix distribution over 2D
  process grid. The functionality and interface is similar to the LAPACK
  wrappers, matrix-matrix multiplication, Cholesky and LU factorizations,
  eigensolvers, SVD, pseudoinverse, save/load in HDF5 format and other
  functionality is implemented. A user can combine the new linear algebra
  with other MPI-parallel algorithms in \dealii{} without the need to worry
  about MPI communicator being divisible exactly into 2D process grid. The
  processes which are not part of the grid are labeled inactive and
  ScaLAPACK routines will not be called on them.
  %
  Additionally, we improved support of LAPACK. We added methods to perform
  rank-1 update/downdate, calculate Cholesky factorization, trace and
  determinant, as well as estimate the reciprocal condition number. We also
  now support configuration with 64-bit BLAS.

\item
  A dedicated sundials module has been created to provide support for the
  SUNDIALS library. SUNDIALS is a SUite of Nonlinear and
  DIfferential/ALgebraic equations Solvers. ARKode, IDA, and KINSOL are
  supported. ARKode is a solver library that provides adaptive-step time
  integration. IDA is a package for the solution of differential-algebraic
  equations systems in the form $F(t,y,y')=0$. KINSOL is solver for nonlinear
  algebraic systems.

\item
  A dedicated optimization/rol module has been created to provide support for
  the Rapid Optimization Library (ROL). ROL is a package for large-scale
  optimization.

\item
  Support for complex-valued vectors is now at the same level as real-valued
  vectors.

\item
  Support for the nanoflann library. nanoflann is a library for building
  KD-trees of datasets and for the fast querying of closest neighbors in
  KD-trees. nanoflann is used to speed up the search of the p nearest neighbors
  of a given point, or searching the points that fall within a radius of a
  target point.

\item
  Support for the Open Asset Import Library (Assimp). Assimp can be used to read
  about 40 different 3D graphics formats. A subset of these formats can be used
  to generate two-dimensional meshes possibly embedded in a three-dimensional
  space.

\item
  Initial support for Gmsh.
  \emph{[--- Do we actually provide any functionality with the GMSH
  executable yet? ---]}
  \marginpar{TODO}

\item
  Initial support for generalized support points: Internal interpolation
  rewritten (support for $H(\text{curl})$ and $H(\text{div})$ conforming
  elements).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Feature 1}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{New non-standard quadrature rules}

A number of non-standard, special-purpose quadrature rules have been
implemented. Among those are quadrature formulas that support
\begin{itemize}
  \item
    truncating standard formulas to simplical domains (\texttt{Qsimplex}),
  \item
    singular transformations of the unit cell to the unit simplex
    (\texttt{QDuffy}),
  \item
    composition of simplical quadrature rules to a combined rule on the
    unit cell (\texttt{QSplit}),
  \item
    transformation of the unit square to polar coordinates
    (\texttt{QTrianglePolar}).
\end{itemize}
These new quadrature rule greatly help to integrate singular domains. They
are mainly used in Boundary Element Methods.

>>>>

\item Interfaces to more external libraries and programs.

@@

\item
  Support for GPU computations.

\item \dealii{} has made extensive use of both the Clang-Tidy \cite{clang-tidy}
  and Coverity Scan \cite{coverity} static analysis tools for detecting bugs
  and other issues in the code. For example, around 260 issues were detected and
  fixed using the latter tool.
      %% > Is there somewhere we can cite for either of these tools? It would
      %% > be nice to recognize the department of homeland security for offering
      %% The contract with homeland security was completed in 2009.

@@

\item New non-standard quadrature rules:
A number of non-standard, special-purpose quadrature rules have been
implemented. Among these are ones for
(i) truncating standard formulas to simplical domains (\texttt{Qsimplex});
(ii) singular transformations of the unit cell to the unit simplex
    (\texttt{QDuffy});
(iii) composition of simplical quadrature rules to a combined rule on the
    unit cell (\texttt{QSplit});
and (iv) transformation of the unit square to polar coordinates
    (\texttt{QTrianglePolar}).
These quadrature rules greatly help when integrating singular
functions or on singular domains. They
are mainly used in Boundary Element Methods.

\item
  Support for complex-valued vectors at the same level as real-valued
  vectors.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Manifolds}

...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Support for particle-in-cell methods}

...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Dedicated support for automatic and symbolic differentiation}

...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{New interfaces to external libraries and programs}

\dealii{} has always tried to leverage high-quality implementations of
algorithms available through other open source software, rather than
re-implementing their functionality. (A list of interfaces to other
packages is given in Section~\ref{sec:cite}.) As part of the current
release, we have written several new interfaces as discussed in the following.

\marginpar{Add references to all of these libraries.}

\paragraph*{ScaLAPACK, a parallel dense linear algebra library.}
  ScaLAPACK provides block-cyclic matrix distribution over 2D process
  grid. The functionality and interface of our wrappers is similar to
  the LAPACK wrappers for serial dense linear algebra, namely
  matrix-matrix multiplication, Cholesky and LU factorizations,
  eigensolvers, SVD, pseudoinverses, and save/load operations using
  the HDF5 format. All of this functionality is available even in
  cases where the number of MPI processes does not exactly divide the
  number of tiles stored in the block-cyclic data distribution.

  As part of this effort, we have also improved LAPACK support: there
  are now methods to perform rank-1 updates/downdates, Cholesky
  factorizations, to compute the trace and determinant, as well as
  estimate the reciprocal condition number. We also now support
  configuration with 64-bit BLAS.

\paragraph*{SUNDIALS, a SUite of Nonlinear and DIfferential/ALgebraic
  Equation Solvers.}
  Solving nonlinear algebraic and differential equations is both a
  common task and one that often requires sophisticated globalization
  algorithms for efficiency and reliability. SUNDIALS provides these
  in a widely used format, both sequentially and in parallel.

  \dealii{} now has interfaces to SUNDIALS's ARKode, IDA, and KINSOL sub-packages.
  ARKode is a solver library that provides adaptive-step time
  integration. IDA is a package for the solution of differential-algebraic
  equations systems in the form $F(t,y,y')=0$. KINSOL is solver for nonlinear
  algebraic systems.

\paragraph*{ROL, a Rapid Optimization Library.}
ROL is a package for large-scale optimization.
\marginpar{Can we add a sentence or two about the ROL interface here?}

\paragraph*{nanoflann, a library for building and querying
  $k$-d trees of datasets.} Operations such as finding the vertex
or cell closest
to a given evaluation point occur frequently in many applications that
use unstructured meshes. While the naive algorithm is linear in the
number of vertices or cells, many such operations can be made
significantly faster by building a $k$-d tree data structure that
recursively subdivides a $k$ dimensional space. The nanoflann library
provides such a data structure and allows querying it, either for
closest points (e.g., when finding the closest vertex) or for
searching the points that fall within a radius of a target point. This
functionality is now available via \dealii{} interfaces.

\paragraph*{Assimp, the Open Asset Import Library.}
  Assimp can be used to read about 40 different 3D graphics formats. A
  subset of these formats can be now be read from within \dealii{} to
  generate two-dimensional meshes, possibly embedded in a
  three-dimensional space.

\paragraph*{Gmsh.}
  \marginpar{Do we actually provide any functionality with the GMSH
  executable yet? If so, complete this part}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Support for GPU computations}

\marginpar{Bruno?}
...

@@
